Metal Enrichment and Stellar Populations of High Redshift Dwarf Galaxies

### 2011-01-15 ms.tex
Adding almost all of the figures.

@@

We use the adaptive mesh refinement (AMR) code
enzo~v2.0\footnote{\texttt{enzo.googlecode.com, changeset
    b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
strong shocks and rarefaction waves.  To resolve minihalos with at
least 100 dark matter (DM) particles and follow the formation of the
first generation of dwarf galaxies, we use a simulation box of 1 Mpc
that has a resolution of $256^3$.  This gives us a DM mass resolution
of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
2^{-0.2l}$, where $l$ is the AMR level, resulting in a
super-Lagrangian behavior.  We also refine on a DM overdensity of $3
\times 2^l$ and always resolve the local Jeans length by at least 4
cells, avoiding artificial fragmentation during gaseous collapses
\citep{Truelove97}.  This simulation has $1.4 \times 10^8$
computational elements and a maximal spatial resolution of 0.1 pc.  We
initialize the simulation with \textsl{grafic} \citep{Bertschinger01}
at $z = 130$ and use the cosmological parameters from the 7-year WMAP
$\Lambda$CDM+SZ+LENS best fit \citep{WMAP7}: $\Omega_M = 0.266$,
$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
0.81$, and $n = 0.963$ with the variables having their usual
definitions.  We stop the simulation at $z=7$.

@@

@@

@@

@@

>>>>

\begin{figure*}
  \epsscale{2}
  \plotone{bmosaic.eps}
  \epsscale{1}
  \caption{\label{fig:evo-mosaic} text.}
\end{figure*}

@@

We use the adaptive mesh refinement (AMR) code
\textsc{enzo~v2.0}\footnote{\texttt{enzo.googlecode.com, changeset
    b86d8ba026d6}} \citep{OShea2004}, which has been modified to use a
HLLC Riemann solver \citep{Toro94_HLLC} for additional stability in
strong shocks and rarefaction waves.  To resolve minihalos with at
least 100 dark matter (DM) particles and follow the formation of the
first generation of dwarf galaxies, we use a simulation box of 1 Mpc
that has a resolution of $256^3$.  This gives us a DM mass resolution
of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
2^{-0.2l}$, where $l$ is the AMR level, resulting in a
super-Lagrangian behavior.  We also refine on a DM overdensity of $3
\times 2^l$ and always resolve the local Jeans length by at least 4
cells, avoiding artificial fragmentation during gaseous collapses
\citep{Truelove97}.  This simulation has $1.4 \times 10^8$
computational elements and a maximal spatial resolution of 0.1 pc.  We
initialize the simulation with \textsc{grafic} \citep{Bertschinger01}
at $z = 130$ and use the cosmological parameters from the 7-year WMAP
$\Lambda$CDM+SZ+LENS best fit \citep{WMAP7}: $\Omega_M = 0.266$,
$\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$, $\sigma_8 =
0.81$, and $n = 0.963$ with the variables having their usual
definitions.  We stop the simulation at $z=7$.

@@

\begin{figure*}
  \plottwo{z7-mosaic0.eps}{z7-mosaic1.eps}
  \caption{\label{fig:z7-mosaic} Redshift 7.}
\end{figure*}

\begin{figure*}
  \plottwo{z8-mosaic0.eps}{z8-mosaic1.eps}
  \caption{\label{fig:z8-mosaic} Redshift 8.}
\end{figure*}

\begin{figure*}
  \plottwo{z10-mosaic0.eps}{z10-mosaic1.eps}
  \caption{\label{fig:z10-mosaic} Redshift 10.}
\end{figure*}

@@

\begin{figure*}
  \plottwo{history0.eps}{history5.eps}
  \caption{\label{fig:massevo} Mass evolution.}
\end{figure*}

@@

\begin{figure}
  \plotone{Zhistory.eps}
  \caption{\label{fig:Zevo} Metal evolution.}
\end{figure}

\begin{figure}
  \plotone{z2.eps}
  \caption{\label{fig:z2} Halo metallicities.}
\end{figure}

\begin{figure}
  \plotone{z3.eps}
  \caption{\label{fig:z3} Halo metallicities.}
\end{figure}

\begin{figure}
  \plotone{ztot.eps}
  \caption{\label{fig:ztot} Halo metallicities.}
\end{figure}

@@

\begin{figure}
  \plotone{mlratios.eps}
  \caption{\label{fig:ML} Mass to light ratios.}
\end{figure}

%\begin{figure}
%  \plotone{sfh.eps}
%  \caption{\label{fig:SFR} Star formation history.}
%\end{figure}
